\textcolor{Navy}{\textsc{Convexity adjustments with a bit of Malliavin}}

### 2023-01-25 Latex/paper.tex
# more modifications

\section{Convexity Adjustment}\label{sec:CA}
In this section, we derive the convexity adjustment for different products. The advantage of using the Malliavin calculus is that it allows us to derive a general representation formula for the convexity adjustment. In order to introduce a general idea of the method. Let define a $Z_t = f(x_t)$. Now, we suppose that $Z_t$ is martingale under the measure $\mathbb{Q}_1$ and that we want to compute $\mathbb{E}^{\mathbb{Q}_2}\left(Z_T \right)$, where $\mathbb{Q}_2$ is a measure such that $\frac{d\mathbb{Q}_2}{d\mathbb{Q}_1} = \lambda_t$.

Since the convexity adjustment is derived for the Cheyette model, it can be applied to all included models, such as the Hull-White model.

@@

where $P_{E}(t,T)$ is the discount factor for the curve $E$ from $t$ to $T$, and $\delta_{t_1,t_2}$ is the year fraction between $t_1$ and $t_2$. Observe that $L_{E}(t, t_1, t_2)$ is a martingale under the forward measure $\mathbb{Q}^{t_2}$. Let us define the conditional future rate as:  

@@

\eqref{forward_rate} and \eqref{future}, we can express the convexity adjustment definition as:%From \eqref{forward_rate} and \eqref{future}, we will define the convexity adjustment as

@@

We use the Clark-Ocone formula with a view to obtaining a general representation formula of the convexity adjustment for futures. Applying \eqref{clark-okone} to 
$L_{E}(t_0,t_1,t_2)$, we obtain
\begin{equation}
L_{E}(t_0,t_1,t_2) = \hat{L}_{E}(t,t_0, t_1, t_2) + \int_{0}^{t_0} \mathbb{E}_{s}\left(D_s L_{E}(t_0,t_1,t_2) \right) dW^{\mathbb{Q}}_s.
Therefore, if we apply $\mathbb{E}^{\mathbb{Q}^{t2}}(\cdot)$ in the last equation, then we get
CA(t, t_0, t_1, t_2) = - \mathbb{E}^{\mathbb{Q}^{t2}}\left(\int_{0}^{t_0} \mathbb{E}^{\mathbb{Q}}_{s}\left(D_s L_{E}(t_0,t_1,t_2) \right) dW^{\mathbb{Q}}_s \right).

@@

Therefore, if we apply Girsanov's theorem to switch to measure $\mathbb{Q}^{t_2}$, we get that

@@

where $\nu(t,T)$ has been defined in (\ref{ois_forward_rate_curve}). Now, from the definition of $L_{E}(t,T)$ we have that

@@

If we use the representation formula (\ref{bond_ois}) we get that

>>>>

\section{Convexity Adjustment}\label{sec:CA}
In this section, we derive the convexity adjustment for different products. The advantage of using the Malliavin calculus is that it allows us to derive a general representation formula . In order to introduce a general idea of the method. Let define a $Z_t = f(x_t)$. Now, we suppose that $Z_t$ is martingale under the measure $\mathbb{Q}_1$ and that we want to compute $\mathbb{E}^{\mathbb{Q}_2}\left(Z_T \right)$, where $\mathbb{Q}_2$ is a measure such that $dW^{\mathbb{Q}_1}_t = dW^{\mathbb{Q}_2}_t +\lambda_t dt$. Then, if we use the Clark-Ocone representation, we have that
\begin{equation*}
f(x_t) = \mathbb{E}^{\mathbb{Q}_1}\left(f(x_t)\right) + \int_{0}^{t} \mathbb{E}^{\mathbb{Q}_1}_s\left( f^{\prime}(x_t) D_s x_t  \right) dW^{\mathbb{Q}_1}_s
\end{equation*}
Now, if we take $\mathbb{E}^{\mathbb{Q}_2}\left( \cdot \right)$ in the previous expression and we use the Girsanov's theorem, we get that
\begin{equation}\label{general_convexity}
\mathbb{E}^{\mathbb{Q}_2}\left( f(x_t) \right) = f(x_0) + \mathbb{E}^{\mathbb{Q}_1} \left(\int_{0}^{t}  \mathbb{E}^{\mathbb{Q}_1}_s\left( f^{\prime}(x_t) D_s x_t  \right) \lambda_s ds \right). 
\end{equation}
The second term, is the convexity adjustment to due to change of measure from $\mathbb{Q}_1$ to $\mathbb{Q}_2$. The differents choice of $f$, $\mathbb{Q}_1$ and $\mathbb{Q}_2$ will allow us to get an approximation of the convexity adjustment for the different case of interest.

@@

where $P_{E}(t,T)$ is the discount factor for the curve $E$ from $t$ to $T$, and $\delta_{t_1,t_2}$ is the year fraction between $t_1$ and $t_2$. Observe that $L_{E}(t, t_1, t_2)$ is a martingale under the forward measure $\mathbb{Q}^{t_2}$. Let us define the future rate as:  

@@

\eqref{forward_rate} and \eqref{future}, then the convexity adjustment definition is:%From \eqref{forward_rate} and \eqref{future}, we will define the convexity adjustment as

@@

@@

Now, if we use (\ref{general_convexity}) with $f(x_t)=L_{E}(t,t_0, t_1, t_2)$, $\mathbb{Q}_1=\mathbb{Q}$, $\mathbb{Q}_1=\mathbb{Q}^{t_2}$ and $\lambda_t = \nu(t,t_2)$,  we get that

@@

where $\nu(t,T)$ has been defined in (\ref{ois_forward_rate_curve}). Now, from the definition of $L_{E}(t,T)$. Now, if we calculate the malliavin derive of $L_{E}(t_0,t_1,t_2)$ we have that

@@

Now from the zero coupon representation formula (\ref{bond_ois}) we get that
